Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
Wording of "Introduction"

This also means that typical usage examples cannot be found from test code.

We agree that type signatures are good abstract document~\cite{free}
but there are many
functions whose behavior cannot be guessed from their names and type
signatures. A good example is \verb|nub :: [a] -> [a]| in 
the Data.List module.

In other programming language communities,
behavior driven development (BDD) is getting much attention, and is
slowly replacing test driven development (TDD).
In BDD, test code is written with specification terminology.
In other words, specification can be used for automatic testing.

>>>>

This also means that typical usage examples is not provided by test code.

We agree that type signatures are good abstract documentation~\cite{free}, but
there are many functions whose behavior cannot be guessed from their names and
type signatures. A good example is \verb|nub :: [a] -> [a]| from {\tt Data.List}.

In other programming language communities,
behavior driven development (BDD) is getting much attention, and is
slowly replacing test driven development (TDD).
In BDD, test code is written with specification terminology.
In other words, specifications can be used for automatic testing.
